Approximation as Differentiation

### 2025-04-16 appendix/notes/cmon-enriched.tex
Enriched functors have a map on objects too.
Some progress on enriched Yoneda embedding.

In the specific setting of a $\CMon$-enriched presheaf $F: \cat{C}^\op \to \CMon$, enrichment means that $F$
preserves the additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual enriched functor properties in \defref{cmon-enriched:enriched-functor}.

@@

\noindent Now suppose $\cat{C}$ is $\mathscr{V}$-enriched with $\mathscr{V}$ monoidal closed; then the
hom-functor $\Hom{\cat{C}}{-}{X}: \cat{C}^\op \to \mathscr{V}$ is itself $\mathscr{V}$-enriched. The

The following diagram commutes because precomposition with the identity is the identity on morphisms:

@@

\noindent and the following by the associativity of composition:

@@

\noindent We then have an enriched version of the Yoneda embedding, namely a functor $\Yoneda_{\mathscr{V}}:
\cat{C} \to \Func{\cat{C}^\op}{\mathscr{V}}_{\mathscr{V}}$ which sends:

\begin{itemize}
\item each object $X$ in $\cat{C}$ to the enriched hom-functor $\Yoneda_{\mathscr{V}}(X) =
\Hom{\cat{C}}{-}{X}: \cat{C}^\op \to \mathscr{V}$
\item each morphism $f: X \to Y$ in $\cat{C}$ to the natural transformation $\Yoneda_{\mathscr{V}}(f)$ where
$\Yoneda_{\mathscr{V}}(f)_Z$ is again $(f \comp -): \Hom{\cat{C}}{Z}{X} \to \Hom{\cat{C}}{Z}{Y}$
\end{itemize}

\noindent and an enriched Yoneda lemma which says that for any $\mathscr{V}$-enriched presheaf $F$ and any
object $X \in \cat{C}$ the hom-object of natural transformations between the $\mathscr{V}$-enriched presheaf
$\Hom{\cat{C}}{-}{X}$ and $F$, which also lives in $\mathscr{V}$, is isomorphic to $F(X)$:

>>>>

In the specific setting of a $\CMon$-enriched presheaf $F: \cat{C}^\op \to \CMon$, enrichment means that $F$
preserves the additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual enriched functor properties from \defref{cmon-enriched:enriched-functor}.

@@

\noindent Now suppose $\cat{C}$ is $\mathscr{V}$-enriched with $\mathscr{V}$ monoidal closed; then the
hom-functor $\Hom{\cat{C}}{-}{X}: \cat{C}^\op \to \mathscr{V}$ is itself $\mathscr{V}$-enriched, sending
objects $Y$ to the hom-object $\Hom{\cat{C}}{Y}{X}$ in $\mathscr{V}$, and providing a family of morphisms
$\Hom{\cat{C}}{-}{X}_{Y,Z} \to \Hom{\mathscr{V}}{\Hom{\cat{C}}{Y}{X}}{\Hom{\cat{C}}{Z}{X}}$ for any $X, Y$ in
$\cat{C}$. The following diagram commutes because precomposition with the identity is the identity on
morphisms:

@@

\noindent and the following commutes by the associativity of composition:

@@

\noindent There exists an enriched version of the Yoneda embedding, namely a functor $\Yoneda_{\mathscr{V}}:
\cat{C} \to \Func{\cat{C}^\op}{\mathscr{V}}_{\mathscr{V}}$ sending objects $X$ to the enriched hom-functor
$\Yoneda_{\mathscr{V}}(X) = \Hom{\cat{C}}{-}{X}: \cat{C}^\op \to \mathscr{V}$ and providing a family of
morphisms $(\Yoneda_{\mathscr{V}})_{X,Y}: \Hom{\cat{C}}{X}{Y} \to
\Hom{\Func{\cat{C}^\op}{\mathscr{V}}_{\mathscr{V}}}{\Hom{\cat{C}}{-}{X}}{\Hom{\cat{C}}{-}{Y}}$.

The enriched Yoneda lemma says that for any $\mathscr{V}$-enriched presheaf $F$ and any object $X \in \cat{C}$
the hom-object of natural transformations between the $\mathscr{V}$-enriched presheaf $\Hom{\cat{C}}{-}{X}$
and $F$, which also lives in $\mathscr{V}$, is isomorphic to $F(X)$:
